manuscript

### 2023-11-21 scripts/manuscript.qmd
I added the scatterplot!

#Data Visualizations

@@

ggplot(communication, aes(gender, ppis_1_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
  labs(x = "Gender",
       y = "Parental Invasive Behaviors Score",
       title = "Boxplot of Parental Invasive Behaviors Score by Gender")

@@

ggplot(communication, aes(gender, ppis_2_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
  labs(x = "Gender",
       y = "Student Defensive Behaviors Score",
       title = "Boxplot of Student Defensive Behaviors Score by Gender")

@@

ggplot(communication, aes(gender, ppis_total, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
  labs(x = "Gender",
       y = "Parental Privacy Invasion Scale Total",
       title = "Boxplot of Parental Privacy Invasion Scale Total by Gender")

@@

ggplot(communication, aes(gender, ss_score, fill=gender)) +
  geom_boxplot() + 
  theme(legend.position="none") +
  labs(x = "Gender",
       y = "Suspicion Scale Score",
       title = "Boxplot of Suspicion Scale Score by Gender")

@@

>>>>

# Data Visualizations

@@

ggplot(communication, aes(gender, ppis_1_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Teacher Invasive Behaviors Score",
       title = "Boxplot of Teacher Invasive Behaviors Score by Gender")

@@

ggplot(communication, aes(gender, ppis_2_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Student Defensive Behaviors Score",
       title = "Boxplot of Student Defensive Behaviors Score by Gender")

@@

ggplot(communication, aes(gender, ppis_total, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Teacher Privacy Invasion Scale Total",
       title = "Boxplot of Teacher Privacy Invasion Scale Total by Gender")

@@

ggplot(communication, aes(gender, ss_score, fill=gender)) +
  geom_boxplot() + 
  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  theme(legend.position="none") +
  labs(x = "Gender",
       y = "Suspicion Scale Score",
       title = "Boxplot of Suspicion Scale Score by Gender")

@@

```{r}
#| label: scatterplot
#| warning: false
#| message: false
#| echo: false

ggplot(comm, aes(ss_score, ppis_total)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(title = "Student's Trustworthiness and Teacher Privacy Invasions", 
       x = "Own Precieved Trustworthiness",
       y = "Teacher Privacy Invasions") +
  theme_minimal()
```
